The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis

### 2022-09-06 docs/submission/manuscript.Rmd

# note: |
#   \vspace{5ex}
#   \textcolor{orange}{\textbf{\emph{NOT PEER-REVIEWED}}}

@@

keywords          : "Motor learning, OPTIMAL theory, Publication bias, Z-curve"
#wordcount         : ""

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

@@

@@

@@

(ref:fig1-caption) \normalfont \footnotesize \textbf{Description of the original meta-analyses.} Diagram outlining the shared and unique inclusion criteria, dependent variable selection, the number of studies screened, and the number of studies included in each meta-analysis.

@@

@@

(ref:fig2-caption) \normalfont \footnotesize \textbf{Results from the robust Bayesian meta-analysis with publication selection model-averaging (RoBMA-PSMA) method.} **(A)** Prior spike and distribution (purple) with 50% of prior probability density concentrated on the null hypothesis and 50% reflecting plausible true effects with *M* = 0 and *SD* = 1. (The x-axis is truncated; the prior did include a small probability of effects larger than 1 and smaller than -1.) The model-averaged posterior distribution of the mean effect (Mu) of **(B)** self-controlled practice on motor learning (blue). The increased height of the spike at mu = 0 reflects increased belief in the null hypothesis. The remaining distribution reflects updated belief in the size and direction of a possible true effect. The mean estimate (*M* = .034) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution of the mean effect of **(C)** enhanced expectancies on motor learning (red). The decreased height of the spike at mu = 0 reflects decreased belief in the null hypothesis. The remaining distribution reflected updated belief in the size and direction of a possible true effect. The mean estimate (*M* = .26) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution generated from an analysis of **(D)** simulated data (green). In the simulation, 49 studies were sampled from a population with a true effect of mu = .54 and no reporting bias. The mean estimate (*M* = .504) for the posterior is represented by the vertical dashed line. Outliers were not included in the self-controlled (*n* = 2) and enhanced expectancies (*n* = 2) models.

@@

(ref:fig3-caption) \normalfont \footnotesize \textbf{Results of the \emph{z}-curve analyses.} Distribution of *z*-values for **(A)** our simulation with 47% results and no reporting bias (green), **(B, left)** self-controlled practice (blue), **(C, left)** enhanced expectancies (red), and **(D, left)** motivational factors combined (purple). Values in the *z*-score distributions for each analysis that are to the right of the significance line (*z* = 1.96; solid, black) are statistically significant with a two-tailed $\alpha$ of .05. Bootstrapped confidence distributions for the expected discovery rate (EDR; dark) and expected replication rate (ERR; light) for **(B, right)** self-controlled practice (blue), **(C, right)** enhanced expectancies (red), and **(D, right)** motivational factors combined (purple). Note, reported CIs include 5 extra points (EDR) and 3 extra points (ERR) added to the quantiles of the bootstrapped distributions in the right panel,  consistent with @bartos2021. The expected discovery rate is the estimated average power of all studies that have been conducted . The expected replication rate is the estimated power of all studies that observed a statistically significant result. The analysis estimated the average statistical power to be 6%, 8%, and 6% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. The estimated conditional power of the statistically significant results was 11%, 33%, and 21% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. Note that a minimum power of 80% (dashed line, black) is often recommended. Outliers were not included in the self-controlled (*n* = 2), enhanced expectancies (*n* = 2), and motivational factors combined (*n* = 4) analyses.

@@

\vfill

@@

\noindent Conceptualization: BM, MFBB, JOP, MWM, MJC  
Data curation: BM, MJC  
Formal analysis: BM  
Funding acquisition: MJC  
Investigation: BM, MFBB, JOP, MWM, MJC  
Methodology: BM, MFBB, JOP, MWM, MJC  
Project administration: BM, MFBB, JOP, MWM, MJC  
Software: BM, MJC  
Supervision: MWM, MJC  
Validation: BM, MJC  
Visualization: BM, MJC  
Writing -- original draft: BM, MFBB, JOP, MWM, MJC  
Writing -- review & editing: BM, MFBB, JOP, MWM, MJC

@@

>>>>

@@

keywords          : "Motor learning, OPTIMAL theory, Motivation, RoBMA, \\emph{Z}-curve, Publication bias"
#wordcount         : ""

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

@@

\newpage
\linespread{0.96}

@@

\linespread{1.75}

@@

(ref:fig1-caption) \linespread{0.96}\normalfont\footnotesize\textbf{Description of the original meta-analyses.} Diagram outlining the shared and unique inclusion criteria, dependent variable selection, the number of studies screened, and the number of studies included in each meta-analysis.

@@

\linespread{1.75}
\normalsize

@@

(ref:fig2-caption) \linespread{0.96}\normalfont\footnotesize\textbf{Results from the robust Bayesian meta-analysis with publication selection model-averaging (RoBMA-PSMA) method.} **(A)** Prior spike and distribution (purple) with 50% of prior probability density concentrated on the null hypothesis and 50% reflecting plausible true effects with *M* = 0 and *SD* = 1. (The x-axis is truncated; the prior did include a small probability of effects larger than 1 and smaller than -1.) The model-averaged posterior distribution of the mean effect (Mu) of **(B)** self-controlled practice on motor learning (blue). The increased height of the spike at mu = 0 reflects increased belief in the null hypothesis. The remaining distribution reflects updated belief in the size and direction of a possible true effect. The mean estimate (*M* = .034) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution of the mean effect of **(C)** enhanced expectancies on motor learning (red). The decreased height of the spike at mu = 0 reflects decreased belief in the null hypothesis. The remaining distribution reflected updated belief in the size and direction of a possible true effect. The mean estimate (*M* = .26) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution generated from an analysis of **(D)** simulated data (green). In the simulation, 49 studies were sampled from a population with a true effect of mu = .54 and no reporting bias. The mean estimate (*M* = .504) for the posterior is represented by the vertical dashed line. Outliers were not included in the self-controlled (*n* = 2) and enhanced expectancies (*n* = 2) models.

@@

(ref:fig3-caption) \linespread{0.96}\normalfont\footnotesize\textbf{Results of the \emph{z}-curve analyses.} Distribution of *z*-values for **(A)** our simulation with 47% results and no reporting bias (green), **(B, left)** self-controlled practice (blue), **(C, left)** enhanced expectancies (red), and **(D, left)** motivational factors combined (purple). Values in the *z*-score distributions for each analysis that are to the right of the significance line (*z* = 1.96; solid, black) are statistically significant with a two-tailed $\alpha$ of .05. Bootstrapped confidence distributions for the expected discovery rate (EDR; dark) and expected replication rate (ERR; light) for **(B, right)** self-controlled practice (blue), **(C, right)** enhanced expectancies (red), and **(D, right)** motivational factors combined (purple). Note, reported CIs include 5 extra points (EDR) and 3 extra points (ERR) added to the quantiles of the bootstrapped distributions in the right panel,  consistent with @bartos2021. The expected discovery rate is the estimated average power of all studies that have been conducted . The expected replication rate is the estimated power of all studies that observed a statistically significant result. The analysis estimated the average statistical power to be 6%, 8%, and 6% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. The estimated conditional power of the statistically significant results was 11%, 33%, and 21% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. Note that a minimum power of 80% (dashed line, black) is often recommended. Outliers were not included in the self-controlled (*n* = 2), enhanced expectancies (*n* = 2), and motivational factors combined (*n* = 4) analyses.

@@

\vspace{3em}

@@

\noindent Conceptualization: BM, MFBB, JOP, MWM, MJC  
\noindent Data curation: BM, MJC  
\noindent Formal analysis: BM  
\noindent Funding acquisition: MJC  
\noindent Investigation: BM, MFBB, JOP, MWM, MJC  
\noindent Methodology: BM, MFBB, JOP, MWM, MJC  
\noindent Project administration: BM, MFBB, JOP, MWM, MJC  
\noindent Software: BM, MJC  
\noindent Supervision: MWM, MJC  
\noindent Validation: BM, MJC  
\noindent Visualization: BM, MJC  
\noindent Writing -- original draft: BM, MFBB, JOP, MWM, MJC  
\noindent Writing -- review & editing: BM, MFBB, JOP, MWM, MJC

@@

\vspace{3em}

### 2022-09-06 docs/submission/manuscript.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  doc, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Motor learning, OPTIMAL theory, Publication bias, Z-curve}
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{graphbox}
\usepackage{tabularray}
\UseTblrLibrary{booktabs}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 2, 3, 3, 1]{Brad McKay, Mariane F.B. Bacelar, Juliana O. Parma, Matthew W. Miller\textsuperscript{$\dagger$}, Michael J. Carter\textsuperscript{$\dagger$}\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Kinesiology, Boise State University}, {School of Kinesiology, Auburn University}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis},
  pdflang={en-EN},
  pdfkeywords={Motor learning, OPTIMAL theory, Publication bias, Z-curve},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\normalfont \footnotesize \textbf{Description of the original meta-analyses.} Diagram outlining the shared and unique inclusion criteria, dependent variable selection, the number of studies screened, and the number of studies included in each meta-analysis.}\label{fig:fig1}
\end{figure}

@@

\caption{\normalfont \footnotesize \textbf{Results from the robust Bayesian meta-analysis with publication selection model-averaging (RoBMA-PSMA) method.} \textbf{(A)} Prior spike and distribution (purple) with 50\% of prior probability density concentrated on the null hypothesis and 50\% reflecting plausible true effects with \emph{M} = 0 and \emph{SD} = 1. (The x-axis is truncated; the prior did include a small probability of effects larger than 1 and smaller than -1.) The model-averaged posterior distribution of the mean effect (Mu) of \textbf{(B)} self-controlled practice on motor learning (blue). The increased height of the spike at mu = 0 reflects increased belief in the null hypothesis. The remaining distribution reflects updated belief in the size and direction of a possible true effect. The mean estimate (\emph{M} = .034) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution of the mean effect of \textbf{(C)} enhanced expectancies on motor learning (red). The decreased height of the spike at mu = 0 reflects decreased belief in the null hypothesis. The remaining distribution reflected updated belief in the size and direction of a possible true effect. The mean estimate (\emph{M} = .26) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution generated from an analysis of \textbf{(D)} simulated data (green). In the simulation, 49 studies were sampled from a population with a true effect of mu = .54 and no reporting bias. The mean estimate (\emph{M} = .504) for the posterior is represented by the vertical dashed line. Outliers were not included in the self-controlled (\emph{n} = 2) and enhanced expectancies (\emph{n} = 2) models.}\label{fig:fig2}
\end{figure}

@@

\caption{\normalfont \footnotesize \textbf{Results of the \emph{z}-curve analyses.} Distribution of \emph{z}-values for \textbf{(A)} our simulation with 47\% results and no reporting bias (green), \textbf{(B, left)} self-controlled practice (blue), \textbf{(C, left)} enhanced expectancies (red), and \textbf{(D, left)} motivational factors combined (purple). Values in the \emph{z}-score distributions for each analysis that are to the right of the significance line (\emph{z} = 1.96; solid, black) are statistically significant with a two-tailed \(\alpha\) of .05. Bootstrapped confidence distributions for the expected discovery rate (EDR; dark) and expected replication rate (ERR; light) for \textbf{(B, right)} self-controlled practice (blue), \textbf{(C, right)} enhanced expectancies (red), and \textbf{(D, right)} motivational factors combined (purple). Note, reported CIs include 5 extra points (EDR) and 3 extra points (ERR) added to the quantiles of the bootstrapped distributions in the right panel, consistent with Bartoš et al. (2022). The expected discovery rate is the estimated average power of all studies that have been conducted . The expected replication rate is the estimated power of all studies that observed a statistically significant result. The analysis estimated the average statistical power to be 6\%, 8\%, and 6\% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. The estimated conditional power of the statistically significant results was 11\%, 33\%, and 21\% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. Note that a minimum power of 80\% (dashed line, black) is often recommended. Outliers were not included in the self-controlled (\emph{n} = 2), enhanced expectancies (\emph{n} = 2), and motivational factors combined (\emph{n} = 4) analyses.}\label{fig:fig3}
\end{figure}

@@

\noindent Conceptualization: BM, MFBB, JOP, MWM, MJC\\
Data curation: BM, MJC\\
Formal analysis: BM\\
Funding acquisition: MJC\\
Investigation: BM, MFBB, JOP, MWM, MJC\\
Methodology: BM, MFBB, JOP, MWM, MJC\\
Project administration: BM, MFBB, JOP, MWM, MJC\\
Software: BM, MJC\\
Supervision: MWM, MJC\\
Validation: BM, MJC\\
Visualization: BM, MJC\\
Writing -- original draft: BM, MFBB, JOP, MWM, MJC\\
Writing -- review \& editing: BM, MFBB, JOP, MWM, MJC

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Motor learning, OPTIMAL theory, Motivation, RoBMA, \emph{Z}-curve, Publication bias}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{graphbox}
\usepackage{tabularray}
\UseTblrLibrary{booktabs}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 2, 3, 3, 1]{Brad McKay, Mariane F.B. Bacelar, Juliana O. Parma, Matthew W. Miller\textsuperscript{$\dagger$}, Michael J. Carter\textsuperscript{$\dagger$}\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Kinesiology, Boise State University}, {School of Kinesiology, Auburn University}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis},
  pdflang={en-EN},
  pdfkeywords={Motor learning, OPTIMAL theory, Motivation, RoBMA, \emph{Z}-curve, Publication bias},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\linespread{0.96}\normalfont\footnotesize\textbf{Description of the original meta-analyses.} Diagram outlining the shared and unique inclusion criteria, dependent variable selection, the number of studies screened, and the number of studies included in each meta-analysis.}\label{fig:fig1}
\end{figure}

@@

\caption{\linespread{0.96}\normalfont\footnotesize\textbf{Results from the robust Bayesian meta-analysis with publication selection model-averaging (RoBMA-PSMA) method.} \textbf{(A)} Prior spike and distribution (purple) with 50\% of prior probability density concentrated on the null hypothesis and 50\% reflecting plausible true effects with \emph{M} = 0 and \emph{SD} = 1. (The x-axis is truncated; the prior did include a small probability of effects larger than 1 and smaller than -1.) The model-averaged posterior distribution of the mean effect (Mu) of \textbf{(B)} self-controlled practice on motor learning (blue). The increased height of the spike at mu = 0 reflects increased belief in the null hypothesis. The remaining distribution reflects updated belief in the size and direction of a possible true effect. The mean estimate (\emph{M} = .034) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution of the mean effect of \textbf{(C)} enhanced expectancies on motor learning (red). The decreased height of the spike at mu = 0 reflects decreased belief in the null hypothesis. The remaining distribution reflected updated belief in the size and direction of a possible true effect. The mean estimate (\emph{M} = .26) for the posterior distribution is represented by the dashed vertical line. The model-averaged posterior distribution generated from an analysis of \textbf{(D)} simulated data (green). In the simulation, 49 studies were sampled from a population with a true effect of mu = .54 and no reporting bias. The mean estimate (\emph{M} = .504) for the posterior is represented by the vertical dashed line. Outliers were not included in the self-controlled (\emph{n} = 2) and enhanced expectancies (\emph{n} = 2) models.}\label{fig:fig2}
\end{figure}

@@

\caption{\linespread{0.96}\normalfont\footnotesize\textbf{Results of the \emph{z}-curve analyses.} Distribution of \emph{z}-values for \textbf{(A)} our simulation with 47\% results and no reporting bias (green), \textbf{(B, left)} self-controlled practice (blue), \textbf{(C, left)} enhanced expectancies (red), and \textbf{(D, left)} motivational factors combined (purple). Values in the \emph{z}-score distributions for each analysis that are to the right of the significance line (\emph{z} = 1.96; solid, black) are statistically significant with a two-tailed \(\alpha\) of .05. Bootstrapped confidence distributions for the expected discovery rate (EDR; dark) and expected replication rate (ERR; light) for \textbf{(B, right)} self-controlled practice (blue), \textbf{(C, right)} enhanced expectancies (red), and \textbf{(D, right)} motivational factors combined (purple). Note, reported CIs include 5 extra points (EDR) and 3 extra points (ERR) added to the quantiles of the bootstrapped distributions in the right panel, consistent with Bartoš et al. (2022). The expected discovery rate is the estimated average power of all studies that have been conducted . The expected replication rate is the estimated power of all studies that observed a statistically significant result. The analysis estimated the average statistical power to be 6\%, 8\%, and 6\% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. The estimated conditional power of the statistically significant results was 11\%, 33\%, and 21\% for self-controlled practice, enhanced expectancies, and motivational factors combined, respectively. Note that a minimum power of 80\% (dashed line, black) is often recommended. Outliers were not included in the self-controlled (\emph{n} = 2), enhanced expectancies (\emph{n} = 2), and motivational factors combined (\emph{n} = 4) analyses.}\label{fig:fig3}
\end{figure}

@@

\noindent Conceptualization: BM, MFBB, JOP, MWM, MJC\\
\noindent Data curation: BM, MJC\\
\noindent Formal analysis: BM\\
\noindent Funding acquisition: MJC\\
\noindent Investigation: BM, MFBB, JOP, MWM, MJC\\
\noindent Methodology: BM, MFBB, JOP, MWM, MJC\\
\noindent Project administration: BM, MFBB, JOP, MWM, MJC\\
\noindent Software: BM, MJC\\
\noindent Supervision: MWM, MJC\\
\noindent Validation: BM, MJC\\
\noindent Visualization: BM, MJC\\
\noindent Writing -- original draft: BM, MFBB, JOP, MWM, MJC\\
\noindent Writing -- review \& editing: BM, MFBB, JOP, MWM, MJC
